SDR enhancement by clouds

### 2024-02-29 article/article.Rmd
Commit 2024-02-29 19:12

---
title:    SDR enhancement by clouds
subtitle: A Short Subtitle
author:
  - name:         Athanasios N. Natsis 
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
    footnote:     footnote one
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
  - name:         Charikleia Meleti
    email:        meleti@auth.gr
    affiliation:  Laboratory of Atmospheric Physics
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date:          last-modified
bibliography:  [bibliography.bib]

output: 
 #  rticles::mdpi_article:
 #    extra_dependencies:  longtable
 #    keep_tex:            yes
  bookdown::word_document2: default
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
---

@@

CEG: continuous group of cloud enhancement cases

@@

The recording of the signal is the one minute average.
Thus we will refer to this time scale as a cloud enhancement event (CE).
Due to the instruments response time.

@@

@@

## Clear sky identification

Use it to find some interesting days to manual check the CE thresholds. No other usage of clear/cloud characterization in CE.

## Criteria for enhancement based on TSI

@@

We used as reference the .... extraterrestrial horizontal irradiance .....

\ref{eq:test}

$$
\text{ETH} = \cos(\theta) \times \text{TSI}_\text{TOA}
$$

$$
\text{GHI} > 999 \text{ETH}
$$

\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{if $\theta \leq `r C4_lowcut_sza`^\circ$}.\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{if $ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}.
\end{cases}\label{eq:test}
\end{equation}

```{r echo=FALSE, fig.cap="", out.width = '100%'}
knitr::include_graphics("../images/climCEmonth-1.png")
```

@@

@@

@@

@@

------------------------------------------------------------------------

## render test

[@Bais1997]

>>>>

---
title:    SDR enhancement by clouds
subtitle: A Short Subtitle
author:
  - Athanasios N. Natsis^[Laboratory of Atmospheric Physics natsisphysicist@gmail.com] 
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
  - name:         Charikleia Meleti
    email:        meleti@auth.gr
    affiliation:  Laboratory of Atmospheric Physics
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2

bibliography:  [bibliography.bib]

date: "`r format(Sys.time(), '%F')`"

header-includes:
  - \usepackage{caption}
  - \usepackage{placeins}
  - \captionsetup{font=small}

output: 
 #  rticles::mdpi_article:
 #    extra_dependencies:  longtable
 #    keep_tex:            yes
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
    bookdown::word_document2: default
---

@@

ECE: extreme cloud enhancement cases one minute over TSI on horizontal plane

CEG: cloud enhancement groups, cases events with consecutive CE

@@

The recording of the signal is the one minute average.
Thus we will refer to this time scale as a cloud enhancement event (CE).
Due to the instruments response time.....

@@

.......

@@

## Criteria for enhancement identification

@@

We used as reference a modelled clear sky approximation,

criteria for cloud enhancement identification are set acording the Equation \ref{eq:CE4}

\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{if $\theta \leq `r C4_lowcut_sza`^\circ$}.\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{if $ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}.
\end{cases}\label{eq:CE4}
\end{equation}
where: ..........

expand: libradtran calculations and modeling

A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane Equation \ref{eq:ECE}

\begin{equation}
\text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
\label{eq:ECE}
\end{equation}

## Thresholds

@@

Reasoning for the selection

Objectivity

Describe set of referce days we used to evalutate

Example of days plot?

... this is more clear to understand and describe ....

\FloatBarrier

@@

## Trend

```{r echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
knitr::include_graphics("../images/daily-12.png")
```

```{r echo=FALSE, fig.cap="Trend of the yearly excess energy"}
knitr::include_graphics("../images/energy-1.png")
```

```{r echo=FALSE, fig.cap="Trend of the excess energy per CE"}
knitr::include_graphics("../images/energy-3.png")
```

\FloatBarrier

## Climatology

```{r echo=FALSE, fig.cap="Distribution of the number of CE cases"}
knitr::include_graphics("../images/climCEmonth-1.png")
```

```{r echo=FALSE, fig.cap="Distribution of CE above reference"}
knitr::include_graphics("../images/distributions-5.png")
```

\FloatBarrier

## Groups stats

```{r echo=FALSE, fig.cap="Distribution of CE groups"}
knitr::include_graphics("../images/groups-1.png")
```

```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
knitr::include_graphics("../images/groups-4.png")
```

```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"}
knitr::include_graphics("../images/groups-6.png")
```

```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"}
knitr::include_graphics("../images/groups-8.png")
```

\FloatBarrier

## Extrene CE above TSI

```{r echo=FALSE, fig.cap="Distribution of the number of ECE cases"}
knitr::include_graphics("../images/climECEmonth-1.png")
```

```{r echo=FALSE, fig.cap="Distribution of ECE above 'clear sky' reference"}
knitr::include_graphics("../images/extremedistributions-2.png")
```

```{r echo=FALSE, fig.cap="Distribution of ECE Irradiance above 'TSI'"}
knitr::include_graphics("../images/extremedistributions-4.png")
```

@@

\FloatBarrier

@@

Compare to other location stats.
max, ECE, distributions ....

Climatology results
